PM Mungbean meta-analysis

### 2021-01-18 02_Preliminary_analysis.Rmd
Update yield box and whisker plot and create Full trial summary table

fungicide_spray_plot <- 
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "DMI spray"))%>%
   group_by(trial_ref, location, year)%>%
   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., colour = spray_treat))+
   geom_boxplot()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   xlab("Trial location and year")+
   ylab(bquote('Mungbean yeild  '*t~ha^-1*''))+
   scale_x_discrete(labels = bw_labels)+
   ylim(0,2.5)+
   scale_colour_usq()+
   labs(colour = "Fungicide treatment")

@@

>>>>

fungicide_spray_plot <- 
   PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   mutate(spray_treat = ifelse(fungicide_ai == "control","control", "Fungicide treated"))%>%
   group_by(trial_ref, location, year)%>%
   ggplot(aes(reorder(trial_ref, grain_yield.t.ha.), grain_yield.t.ha., fill = spray_treat))+
   geom_boxplot()+
   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   xlab("Trial location and year")+
   ylab(bquote('Mungbean yield  '*t~ha^-1*''))+
   scale_x_discrete(labels = bw_labels)+
   ylim(0,2.5)+
   scale_fill_grey(start = 1, end = 0.7)+
   labs(colour = "Fungicide treatment")+
   guides(fill = guide_legend(title = "Treatment"))

fungicide_spray_plot
#ggsave("paper/figures/Fig1_trial_yield_bw.png")
```

@@

#### Full trial summary

```{r Full_Trial_Summary_table}
PM_MB_dat %>%
   filter(
      fungicide_ai == "control" |
         fungicide_ai == "tebuconazole" |
         fungicide_ai == "propiconazole"
   ) %>%
   mutate(PM_sev_control = case_when(fungicide_ai == "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_sev_treat = case_when(fungicide_ai != "control" ~ PM_final_severity,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_control = case_when(fungicide_ai == "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%
   mutate(PM_y_treat = case_when(fungicide_ai != "control" ~ grain_yield.t.ha.,
                                     TRUE ~ NA_real_)) %>%

   # filter(location == "Bongeen_1")%>%
   # select(PM_sev_treat,
   #        trial_ref,
   #          location,
   #          year,
   #          planting_date,
   #          first_sign_disease)

   group_by(trial_ref,
            location,
            year,
            planting_date,
            first_sign_disease) %>%
   summarise(n = n(),
             m_PM_sev_control = mean(PM_sev_control, na.rm = TRUE),
             min_PM_sev = min(PM_sev_treat, na.rm = TRUE),
             max_PM_sev = max(PM_sev_treat, na.rm = TRUE),
             m_PM_yeild_control = mean(PM_y_control, na.rm = TRUE),
             min_PM_yeild = min(PM_y_treat, na.rm = TRUE),
             max_PM_yeild = max(PM_y_treat, na.rm = TRUE)
             )%>%
   filter(min_PM_sev < 10) # anything exceeding 9 is off the scale and should be removed due to it being the result of min(NA, na.rm = T) ie. Inf
